Future challenges for Research Software Engineering

### 2025-09-24 future_challenges_for_RSEng.tex
less hope

We hope that the standard of research software will have risen across the board,
enabling easier reuse of prior software outputs in new research.
We also hope that a cultural change is taking place to recognise research software
as an integral part of science that it is widely recognised and rewarded across
academia and is supported by political actors.

>>>>

We anticipate that the standard of research software will have risen across the board,
enabling easier reuse of prior software outputs in new research.
We hope that a cultural change is taking place to recognise research software
as an integral part of science that it is widely recognised and rewarded across
academia and is supported by political actors.
